Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-17 paper/paper.tex
Distributed bits in the intro

Main technical contribution of this paper is the lower bound $\Omega(k\cdot\ell)$ (Section~\ref{sec:lowerbound}) for the competitive ratio of any deterministic algorithm for online Balanced RePartition problem..
The best known lower bound so far was $\Omega(k)$ \cite{repartition-disc}
which involves only two cluster.

So far, the competitive ratio of the best known algorithm was the component-based algorithm with the ratio $O(k^2\cdot \ell^2)$ \cite{repartition-disc}.
By applying classic rent-or-buy technique, we obtained an optimal algorithm for $k=3$, that we present in Section~\ref{sec:k3}.

>>>>

Main technical contribution of this paper is the lower bound $\Omega(k\cdot\ell)$ for the competitive ratio of any deterministic algorithm for online Balanced RePartition problem (see Section~\ref{sec:lowerbound}).
The best known lower bound so far was $\Omega(k)$ \cite{repartition-disc}
which involves only two clusters.

So far, the competitive ratio of the best known algorithm was the component-based algorithm with the ratio $O(k^2\cdot \ell^2)$~\cite{repartition-disc}.
By applying classic rent-or-buy technique, we obtained an optimal algorithm for $k=3$, that we present in Section~\ref{sec:k3}.
